This is an example of article title

### 2024-05-16 paper/paper.tex
Add comments with infos from JOSS docs
first draft of begin of summary

@@

>>>>

%%---- definition of custom commands
\newcommand{\abs}[1]{\left|#1\right|}
\newcommand{\vb}{\boldsymbol}
%%----

@@

\texttt{Peridynamics.jl} is an open source implementation of the nonlocal continuum mechanics formulation by Silling (ref?).
In peridynamics, a body is described by material points and, based on interactions between them, internal force densities are calculated. 
The equation of motion reads
\begin{equation}
    \varrho \, \vb{\ddot{u}}(\vb{X},t) = \vb{b}^{\mathrm{int}}(\vb{X},t) + \vb{b}^{\mathrm{ext}}(\vb{X},t) \qquad \forall \vb{X} \in \mathcal{B}_0, \; t \geq 0 \; ,
\end{equation} 
with the mass density $\varrho$, the point acceleration vector $\vb{\ddot{u}}$, and the point force density vectors $\vb{b}^{\mathrm{int}}$ and $\vb{b}^{\mathrm{ext}}$. 
In the original bond-based formulation (BB), the internal force density is calculated by
\begin{equation}
    \vb{b}^{\mathrm{int}}(\vb{X},t) = \int_\mathcal{H} \vb{f} \; \mathrm{d}V' \; ,
\end{equation}
with the \emph{pairwise force function} $\vb{f}$, which is evaluated for each material point $\vb{X}^i$ and depends on the deformation of the bonds to each point in its neighborhood $\mathcal{H}$.
These point families contain each point within a distance $\delta$, also called horizon.

To overcome the restrictions of the BB formulation with only one determinable material parameter, the state-based formulation was established.
Here not only the bonds to neighboring material points, but also the states of neighboring points influence the internal force density $\vb{b}^{\mathrm{int}}$ of each material point.
The equation reads
\begin{equation}
    \vb{b}^{\mathrm{int}} (\vb{X},t) = \int_\mathcal{H} \vb{t} - \vb{t}' \; \mathrm{d}V' \; ,
\end{equation}
with the force vector states $\vb{t}=\vb{t}(\vb{\Delta X}, t)$ and $\vb{t}'=\vb{t}(-\vb{\Delta X}, t)$.

The \texttt{Peridynamics.jl} package enables users to perform peridynamic simulations
